The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-06-06 paper.tex
improve table

\section{Description of ANNOdc}\label{sec:core}
% Definition/Beschreibung der Kern-Konzepte/Module und -Relationen mit Beispielen, GFO-Einbettung
\begin{figure}[h]
\includegraphics[width=\textwidth]{img/core.pdf}
\caption{ANNOdc ontology}\label{fig:core}
\end{figure}

>>>>

\section{Description and Foundation of ANNOdc}\label{sec:core}
% Definition/Beschreibung der Kern-Konzepte/Module und -Relationen mit Beispielen, GFO-Einbettung
\begin{figure}[h]
\includegraphics[width=\textwidth]{img/core.pdf}
\caption{ANNOdc ontology}\label{fig:core}
\end{figure}

\begin{table}[htbp]
  \centering
  \caption{Table Title}
  \begin{tabular}{llll}
    \toprule
	ANNOdc class					&Examples				&FMA equivalent / ID						&GFO superclass	\\
	\midrule
	Anatomical entity				&						&Physical anatomical entity fma61775\\
	Anatomical structure			&						&Material anatomical entity	fma67165		&Material object\\							
	Spatial anatomical entity		&						&immaterial anatomical entity fma:fma67112	&Space entity\\
	Anatomical space				&						&											&Space region\\
	Anatomical surface				&Median Plane			&Anatomical surface fma24137				&Surface region\\
	Anatomical line					&Mandibular Angle (ppam dexter-go dexter-piam dexter), Sagittal Axis	&Anatomical line fma9657	&Line region\\
	Anatomical point				&Gonion					&Anatomical point							&Point region\\
	Anatomical plane				&Median Plane			&Anatomical plane fma242982\\
	Anatomical axis		 			&Sagittal Axis\\
	Skeleton						&						&Skeleton fma:fma23875\\
	Bone structure\\
	Bone							&Mandibula			&Bone organ fma:fma5018					&-				\\
	Bone part					&-					&Protuberantia mentalis					&Related to Segment of bone organ fma:fma281808, Zone of bone organ fma:fma10483\\
	Bone compound				&Cranium				&Comparable to union of Skeletal system fma:fma23881 and subdivision of skeletal system fma:fma85544&-\\
	Tooth structure				&Dentes Permanentes	&Permanent teeth (fma:fma75152; TA2ID:913)&Tooth			\\
	Tooth						&Dens caninus			&Tooth fma:fma12516						&-				\\
	Tooth part					&Cuspis dentis		&fma:fma56481; TA2ID:925					&-				\\
	Phenotype					&Height, Sex			&-										&Anatomical Property\\
	Attributive					&Anatomical relation, e.g., Has\_shape relation&-							&Attributive	\\
	Anatomical qualitative coordinate&Superior, lateral, medial, posterior&Anatomical Property	&Relator		\\
\bottomrule
\end{tabular}
\end{table}
